---
title: "Homework 5"
author: "Kendall Pollard"
format:
  pdf:
    output-file: "pollard-k-hwk5-1"
    output-ext:  "pdf"
    header-includes:
      - \usepackage{float}
      - \floatplacement{table}{H}
---


```{r}
#| include: false

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, readr, readxl, hrbrthemes, fixest,
               scales, gganimate, gapminder, gifski, png, tufte, plotly, OECD,
               ggrepel, survey, foreign, devtools, pdftools, kableExtra, modelsummary,
               kableExtra)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
```


```{r}
#| include: false
#| eval: true
load("Hw5_workspace.Rdata")
```

Here is the link to my GitHub Repository:

Here are my answers for Homework 5. I do the coding in a separate `R` script, but here is the cleaned-up version. I run the analysis separately, save the workspace with only the summary stats, figures, and tables that I need, and then load the workspace in the final qmd. My analysis file with answers and code to all the questions is available in the analysis folder. 

\newpage 

\vspace{.2in}
\noindent 1. Plot the share of the adult population with direct purchase health insurance over time. <br>

```{r}
#| echo: false
#| label: directpurchase
#| fig-cap: Question 1 Graph

question1
```


\newpage 

\vspace{.2in}
\noindent 2. Discuss the reduction in direct purchase health insurance in later years. Can you list a couple of policies that might have affected the success of the direct purchase insurance market? <br>

After 2016, it seems that direct purchase health insurance declined. 


\newpage 

\vspace{.2in}
\noindent 3. Plot the share of the adult population with Medicaid over time. <br>

```{r}
#| echo: false
#| label: Medicaid
#| fig-cap: Question 3 Graph

question3
```


\newpage 

\vspace{.2in}
\noindent 4. Plot the share of uninsured over time, separately by states that expanded Medicaid in 2014 versus those that did not. Drop all states that expanded after 2014. <br>

```{r}
#| echo: false
#| label: Medicaid2014
#| fig-cap: Question 4 Graph

question4
```

\newpage 

\vspace{.2in}
\noindent 5. Calculate the average percent of uninsured individuals in 2012 and 2015, separately for expansion and non-expansion states. Present your results in a basic 2x2 DD table. <br>

```{r} 
#| echo: false
#| label: uninsured20122015
#| tbl-cap: "Uninsured in 2012 and 2015"

library(kableExtra)
options(knitr.kable.NA = 0)
knitr::kable(avg_did, 
             col.names=c("expand_ever", "avg_diff_uninsured"),
             format.args=list(big.mark=","), booktabs = TRUE) %>%
             kable_styling(latex_options=c("scale_down"))

```

\newpage 

\vspace{.2in}
\noindent 6. Estimate the effect of Medicaid expansion on the uninsurance rate using a standard DD regression estimator, again focusing only on states that expanded in 2014 versus those that never expanded. <br>

```{r}
#| echo: false
#| label: DD6
#| tbl-cap: Question 6 Table


modelsummary(list("DD (2014)" = dd.ins.reg),
                          shape = term + statistic ~ model, 
                          gof_map = NA,
                          coef_omit = 'Intercept')
```

\newpage 

\vspace{.2in}
\noindent 7. Include state and year fixed effects in your estimates. Try using the lfe or fixest package to estimate this instead of directly including the fixed effects. <br>

```{r}
#| echo: false
#| label: DD7
#| tbl-cap: Question 7 Table



```


\newpage 

\vspace{.2in}
\noindent 8. Repeat the analysis in question 7 but include all states (even those that expanded after 2014). Are your results different? If so, why? <br>

```{r}
#| echo: false
#| label: DD8
#| tbl-cap: Question 8 Table

```



\newpage 

\vspace{.2in}
\noindent 9. Provide an “event study” graph showing the effects of Medicaid expansion in each year. Use the specification that includes state and year fixed effects, limited to states that expanded in 2014 or never expanded. <br>

```{r}
#| echo: false
#| label: question9
#| fig-cap: Question 9 Graph


iplot(mod.twfe9, 
                   xlab = 'Time to treatment',
                   main = 'Event study')
```


\newpage 

\vspace{.2in}
\noindent 10. Repeat part 9 but again include states that expanded after 2014. Note: this is tricky…you need to put all states onto “event time” to create this graph. <br>


```{r}
#| echo: false
#| label: question10
#| fig-cap: Question 10 Graph


iplot(mod.twfe10, 
                     xlab = 'Time to treatment',
                     main = 'Event study')

```




